A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-27 paper.tex
Wrote most of the prose for evaluation, still needs results

\documentclass{llncs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{fixltx2e}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{trees}
\usetikzlibrary{positioning}

@@

\begin{algorithm}
    \caption{Tree formulas for Controller and Environment respectively}
    \label{alg:treeFormula}
    \begin{algorithmic}[1]
        \Function{treeFormula}{gt}
        \If{$\Call{rank}{gt} = 0$}
        \State \Return{ $\lnot \Call{E}{x^{gt}}$ }
        \Else
        \State \Return{ $\lnot \Call{E}{x^{gt}} \land \bigwedge_{n \in \Call{succ}{gt}}(\Call{$\delta$}{n} \land \Call{label}{n} \land \Call{treeFormula}{n})$ }
        \EndIf
        \EndFunction
        \algstore{tf1}
    \end{algorithmic}

    \begin{algorithmic}[1]
        \algrestore{tf1}
        \Function{\textoverline{treeFormula}}{gt}
        \If{$\Call{rank}{gt} = 0$}
        \State \Return{\Call{E}{$x^{gt}$}}
        \Else
        \State \Return{ $\Call{E}{x^{gt}} \lor \bigvee_{n \in \Call{succ}{gt}}(\Call{$\delta$}{n} \land \Call{label}{n} \land \Call{\textoverline{treeFormula}}{n})$ }
        \EndIf
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

We evaluate our approach on the benchmarks of the 2015 synthesis competition
(SYNTCOMP'15).

>>>>

\documentclass{llncs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{fixltx2e}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{trees}
\usetikzlibrary{positioning}

@@

\begin{algorithm}
    \caption{Tree formulas for Controller and Environment respectively}
    \label{alg:treeFormula}
    \begin{algorithmic}[1]
        \Function{treeFormula}{$T$}
        \If{$\Call{rank}{T} = 0$}
        \State \Return{ $\lnot \Call{E}{X_{T}}$ }
        \Else
        \State \Return{$\lnot \Call{E}{X_{T}} \land$ \\
            $$\bigwedge_{n \in \Call{succ}{T}}(\Call{$\delta$}{X_n, U_n, C_n, X'_n} \land \Call{label}{n} \land \Call{treeFormula}{n})$$
        }
        \EndIf
        \EndFunction
        \algstore{tf1}
    \end{algorithmic}

    \begin{algorithmic}[1]
        \algrestore{tf1}
        \Function{\textoverline{treeFormula}}{$T$}
        \If{$\Call{rank}{T} = 0$}
        \State \Return{\Call{E}{$X_{T}$}}
        \Else
        \State \Return{ $\Call{E}{X_{T}} \lor$ \\
        $$\bigvee_{n \in \Call{succ}{T}}(\Call{$\delta$}{X_n, U_n, C_n, X'_n} \land \Call{label}{n} \land \Call{\textoverline{treeFormula}}{n})$$ }
        \EndIf
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

We evaluate our approach on the benchmarks of the 2015 synthesis competition
(SYNTCOMP'15). Each benchmark comprises of controllable and uncontrollable
inputs to a circuit that assigns values to latches. One latch is configured as
the error bit that determines the winner of the safety game. The benchmark
suite is a collection of both real-world and toy specifications including
generalised buffers, AMBA bus controllers, device drivers, and converted LTL
formulas.  Descriptions of many of the benchmark families used can be found in
the 2014 competition report~\cite{jacobs2015}.

The implementation of our algorithm uses \textsc{Glucose}~\cite{audemard2014}
for SAT solving and \textsc{Periplo}~\cite{rollini2013} for interpolant
generation. We compared our implementation to two solvers that competed in the
sequential realisability track of SYNTCOMP'15.  \textsc{Simple BDD
Solver}~\cite{walker2014} because it had the best results in the track, and
\textsc{Demiurge}~\cite{bloem2014} because it was the only SAT-based tool to
compete. The benchmarks were run on a cluster of Intel Quad Core Xeon E5405
CPUs with 16GB of memory. Each solver was allowed exclusive access to a node
for one hour to solve an instance.

INSERT GRAPHS

Our implementation was able to solver 103 out of the 250 specification in the
alloted time, including 10 instances that were unable to be solved by any other
solver including all other solvers in SYNTCOMP'15. \textsc{Simple BDD Solver}
and \textsc{Demiurge} were able to solve X and Y respectively. Something about
us vs BDDs and us vs demiurge with numbers of specs.

Four of the previously unsolved instances are device driver instances and
another five are toy examples. This supports the hypothesis that different game
solving methodologies perform better on certain classes of specifications.
